---
title: "Replication Materials for: 'Funding and Favorability: Exploring the Relationship Between Candidate Favorability Ratings and Fundraising Locale in U.S. Senate Election'"
author: 
  - AlexaBarnes^[American University]
date: "2020-12-09"
---

```{r Setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
#Install Preliminary Packages
```{r}
install.packages("devtools")
library(usethis)
library(devtools)
```
```{r}
devtools::install_github("stephenholzman/tidyusafec", force = TRUE)
```
#Load Packages
```{r Packages, echo=TRUE}
library(readr)
library(dplyr)
library(tidyusafec)
library(tidyverse)
library(utils)
library(repmis)
```
#Define API Key
```{r API, echo=FALSE, include=FALSE}
## In this section, you will need to supply an API Key. For more information, visit: https://api.open.fec.gov/developers/.

API_KEY <-
```
#Loading Campaign Data
```{r Read CSV, echo=TRUE}
source_data("https://github.com/AlexaGBarnes/FundingFavorability/blob/main/FundingFavorabilityObjects.RData?raw=true")
Senate_Favorability <- Campaigns
```
#Create Year Groups
```{r Concatenate Committees by Year, echo=TRUE, cache=TRUE}
Committees2004 <- subset(Senate_Favorability, two_year_transaction_period == "2004", select = committee_ID)
Committees2006 <- subset(Senate_Favorability, two_year_transaction_period == "2006", select = committee_ID)
Committees2008 <- subset(Senate_Favorability, two_year_transaction_period == "2008", select = committee_ID)
Committees2010 <- subset(Senate_Favorability, two_year_transaction_period == "2010", select = committee_ID)
Committees2012 <- subset(Senate_Favorability, two_year_transaction_period == "2012", select = committee_ID)
Committees2014 <- subset(Senate_Favorability, two_year_transaction_period == "2014", select = committee_ID)
Committees2016 <- subset(Senate_Favorability, two_year_transaction_period == "2016", select = committee_ID)
Committees2018 <- subset(Senate_Favorability, two_year_transaction_period == "2018", select = committee_ID)
```
#Pull Itemized Contributions by Year
```{r, Contributions for 2004, cache = TRUE}
StorageD42004 <- tibble()
Contributions2004 <- for(i in 1:nrow(Committees2004)){
    out <- get_itemized_contributions(committee_id = Committees2004$committee_ID[i], 
                    api_key = API_KEY, 
                    data_structure = "tidy", 
                    max_date = "11/2/2004", 
                    min_date = "01/01/2004")
  StorageD42004 <- bind_rows(StorageD42004, out)
  Sys.sleep(20)}
tibble(StorageD42004)
saveRDS(StorageD42004, file = "ItemizedContributions2004.RDS")
tibble(StorageD42004)
```
```{r Contributions for 2006, cache=TRUE}
StorageD42006 <- tibble()
Contributions2006 <- for(i in 1:nrow(Committees2006)){
    out <- get_itemized_contributions(committee_id = Committees2006$committee_ID[i], 
                    api_key = API_KEY, 
                    data_structure = "tidy", 
                    max_date = "11/7/2006", 
                    min_date = "01/01/2006")
  StorageD42006 <- bind_rows(StorageD42006, out)
  Sys.sleep(20)}
tibble(StorageD42006)
saveRDS(StorageD42006, file = "ItemizedContributions2006.RDS")
tibble(StorageD42006)
```
```{r Contributions for 2008, cache=TRUE}
StorageD42008 <- tibble()
Contributions2008 <- for(i in 1:nrow(Committees2008)){
    out <- get_itemized_contributions(committee_id = Committees2008$committee_ID[i], 
                    api_key = API_KEY, 
                    data_structure = "tidy", 
                    max_date = "11/04/2008", 
                    min_date = "01/01/2008")
  StorageD42008 <- bind_rows(StorageD42008, out)
  Sys.sleep(20)}
tibble(StorageD42008)
saveRDS(StorageD42008, file = "ItemizedContributions2008.RDS")
```
```{r Contributions for 2010, cache=TRUE}
StorageD42010 <- tibble()
Contributions2010 <- for(i in 1:nrow(Committees2010)){
    out <- get_itemized_contributions(committee_id = Committees2010$committee_ID[i], 
                    api_key = API_KEY, 
                    data_structure = "tidy", 
                    max_date = "11/02/2010", 
                    min_date = "01/01/2010")
  StorageD42010 <- bind_rows(StorageD42010, out)
  Sys.sleep(60)}
tibble(StorageD42010)
saveRDS(StorageD42010, file = "ItemizedContributions2010.RDS")
```
```{r Contributions for 2012, message=TRUE, cache=TRUE, paged.print=TRUE}
StorageD42012 <- tibble()
Contributions2012 <- for(i in 1:nrow(Committees2012)){
    out <- get_itemized_contributions(committee_id = Committees2012$committee_ID[i], 
                    api_key = API_KEY, 
                    data_structure = "tidy", 
                    max_date = "11/06/2012", 
                    min_date = "01/01/2012")
  StorageD42012 <- bind_rows(StorageD42012, out)
  Sys.sleep(60)}
tibble(StorageD42012)
saveRDS(StorageD42012, file = "ItemizedContributions2012.RDS")
StorageD42010 %>% count(committee_id)
```
```{r Contributions for 2014, cache=TRUE}
StorageD42014 <- tibble()
Contributions2014 <- for(i in 1:nrow(Committees2014)){
    out <- get_itemized_contributions(committee_id = Committees2014$committee_ID[i], 
                    api_key = API_KEY, 
                    data_structure = "tidy", 
                    max_date = "11/04/2014", 
                    min_date = "01/01/2014")
  StorageD42014 <- bind_rows(StorageD42014, out)
  Sys.sleep(60)}
tibble(StorageD42014)
saveRDS(StorageD42014, file = "ItemizedContributions2014.RDS")
```
```{r Contributions for 2016, cache=TRUE}
StorageD42016 <- tibble()
Contributions2016 <- for(i in 1:nrow(Committees2016)){
    out <- get_itemized_contributions(committee_id = Committees2016$committee_ID[i], 
                    api_key = API_KEY, 
                    data_structure = "tidy", 
                    max_date = "11/08/2016", 
                    min_date = "01/01/2016")
  StorageD42016 <- bind_rows(StorageD42016, out)
  Sys.sleep(300)}
tibble(StorageD42016)
saveRDS(StorageD42016, file = "ItemizedContributions2016.RDS")
```
```{r Contributions for 2018, cache=TRUE}
StorageD42018 <- tibble()
Contributions2018 <- for(i in 1:nrow(Committees2018)){
    out <- get_itemized_contributions(committee_id = Committees2018$committee_ID[i], 
                    api_key = API_KEY, 
                    data_structure = "tidy", 
                    max_date = "11/06/2018", 
                    min_date = "01/01/2018")
  StorageD42016 <- bind_rows(StorageD42016, out)
  Sys.sleep(300)}
tibble(StorageD42018)
saveRDS(StorageD42018, file = "ItemizedContributions2018.RDS")
```
```{r}
SkinnyContributions <- rbind
SkinnyContributionsUnique <- unique(StackedContributions)
```
#Rename Year Groups
```{r}
Cont2004 <- StorageD42004
Cont2006 <- StorageD42006
Cont2008 <- StorageD42008
Cont2010 <- StorageD42010
Cont2012 <- StorageD42012
Cont2014 <- StorageD42014
Cont2016 <- StorageD42016
Cont2018 <- StorageD42018
```
#Generate Campaigns Table
```{r Load Senate Favorability}
CampaignswithFav <- Campaigns %>% mutate(Funding_Favorability = paste(committee_ID, two_year_transaction_period))
tibble(CampaignswithFav)
```

#Append Funding_Favorability Key and Reduce Years
```{r Combine Contributions and Attach Funding_Favorability}
Skinny4 <- Cont2004 %>% select(sub_id, image_number, link_id, contributor_state, report_year, pdf_url, contributor_name, two_year_transaction_period, contribution_receipt_amount, committee_id) %>% mutate(Funding_Favorability = paste(committee_id, two_year_transaction_period))
tibble(Skinny4)
```
```{r Combine Contributions and Attach Funding_Favorability}
Skinny6 <- Cont2006 %>% select(sub_id, image_number, link_id, contributor_state, report_year, pdf_url, contributor_name, two_year_transaction_period, contribution_receipt_amount, committee_id) %>% mutate(Funding_Favorability = paste(committee_id, two_year_transaction_period))
tibble(Skinny6)
```
```{r Combine Contributions and Attach Funding_Favorability}
Skinny8 <- Cont2008 %>% select(sub_id, image_number, link_id, contributor_state, report_year, pdf_url, contributor_name, two_year_transaction_period, contribution_receipt_amount, committee_id) %>% mutate(Funding_Favorability = paste(committee_id, two_year_transaction_period))
tibble(Skinny8)
```
```{r Combine Contributions and Attach Funding_Favorability}
Skinny10 <- Cont2010 %>% select(sub_id, image_number, link_id, contributor_state, report_year, pdf_url, contributor_name, two_year_transaction_period, contribution_receipt_amount, committee_id) %>% mutate(Funding_Favorability = paste(committee_id, two_year_transaction_period))
tibble(Skinny10)
```
```{r Combine Contributions and Attach Funding_Favorability}
Skinny12 <- Cont2012 %>% select(sub_id, image_number, link_id, contributor_state, report_year, pdf_url, contributor_name, two_year_transaction_period, contribution_receipt_amount, committee_id) %>% mutate(Funding_Favorability = paste(committee_id, two_year_transaction_period))
tibble(Skinny12)
```
```{r Combine Contributions and Attach Funding_Favorability}
Skinny14 <- Cont2014 %>% select(sub_id, image_number, link_id, contributor_state, report_year, pdf_url, contributor_name, two_year_transaction_period, contribution_receipt_amount, committee_id) %>% mutate(Funding_Favorability = paste(committee_id, two_year_transaction_period))
tibble(Skinny14)
```
```{r Combine Contributions and Attach Funding_Favorability}
Skinny16 <- Cont2016 %>% select(sub_id, image_number, link_id, contributor_state, report_year, pdf_url, contributor_name, two_year_transaction_period, contribution_receipt_amount, committee_id) %>% mutate(Funding_Favorability = paste(committee_id, two_year_transaction_period))
tibble(Skinny16)
```
```{r Combine Contributions and Attach Funding_Favorability, cache = TRUE}
Skinny18 <- Cont2018 %>% select(sub_id, image_number, link_id, contributor_state, report_year, pdf_url, contributor_name, two_year_transaction_period, contribution_receipt_amount, committee_id) %>% mutate(Funding_Favorability = paste(committee_id, two_year_transaction_period))
tibble(Skinny18)
```
#RBind into Stacked Contributions
```{r}
StackedContributions <- rbind(StackedCont04to16, Skinny18, deparse.level = 1, make.row.names = TRUE, stringsAsFactors = default.stringsAsFactors(), factor.exclude = TRUE)
tibble(StackedContributions)
saveRDS(StackedContributions, file = "StackedContributions_All.RDS")
```
#Inner join and append State_Match
```{r, cache = TRUE}
JointContributions <- SkinnyContributionsUnique %>% inner_join(CampaignswithFav, by = "Funding_Favorability")
tibble(JointContributions)
WithMatch <- JointContributions %>% mutate(State_Match = (contributor_state == state))
tibble(WithMatch) 
count(WithMatch$State_Match)
```
#Subset In-State and Out of State
```{r}
InState <- WithMatch %>% subset(State_Match == "TRUE", select = c(Funding_Favorability, link_id, sub_id, image_number, contribution_receipt_amount,  two_year_transaction_period.x)) %>% mutate(InStateCont = contribution_receipt_amount)

OutofState <- WithMatch %>% subset(State_Match == "FALSE", select = c(Funding_Favorability, link_id, sub_id, image_number, contribution_receipt_amount,  two_year_transaction_period.x)) %>% mutate(OutofStateCont = contribution_receipt_amount)

InStateSummarized <- aggregate(InState$contribution_receipt_amount,  by=list(Funding_Favorability = InState$Funding_Favorability), FUN=sum) %>% dplyr::rename(InState_Contributions = x)

tibble(InStateSummarized)

OutofStateSummarized <- aggregate(OutofState$contribution_receipt_amount,  by=list(Funding_Favorability = OutofState$Funding_Favorability), FUN=sum) %>% dplyr::rename(OutofState_Contributions = x)

tibble(OutofStateSummarized)
```
#Join Summaries to Senate_Favorability
```{r}
LocalizedContributions <- InStateSummarized %>% inner_join(OutofStateSummarized, by = "Funding_Favorability") %>% mutate(Itemized_Contributions = (OutofState_Contributions + InState_Contributions)) %>% mutate(InState_Proportion = InState_Contributions/Itemized_Contributions) %>% mutate(OutofState_Proportion = OutofState_Contributions/Itemized_Contributions) %>% mutate(validate = (OutofState_Proportion + InState_Proportion))

ContributionSummaries <- LocalizedContributions %>% inner_join(CampaignswithFav, by = "Funding_Favorability")

tibble(LocalizedContributions)
tibble(ContributionSummaries)

saveRDS(ContributionSummaries, file = "ContributionSummaries.RDS")
```
#Linear Regression without Controls
```{r echo = FALSE, include=FALSE, message=FALSE}
no_controls <- lm(favorability ~ InState_Proportion, data = ContributionSummaries)
summary(no_controls)
```
#Linear Regression with Controls
```{r echo = FALSE, include=FALSE, message=FALSE}
with_controls <- lm(favorability ~ InState_Proportion + party + pollster + two_year_transaction_period, data = ContributionSummaries)
summary(with_controls)
```
